The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Tiny changes to paper

\begin{abstract}
   This note describes the \emph{Macaulay2} package \emph{FrobeniusThresholds}.
   This package is designed to estimate and calculate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in prime characteristic commutative algebra.
\end{abstract}

@@

Unfortunately, the $F$-pure threshold is typically difficult to calculate, even in many concrete cases.   It is also not so well understood from the perspective of reduction to prime characteristic.   Nevertheless, $F$-pure thresholds have been the focus of intense study over the past fifteen years, and the \emph{Macaulay2} package \emph{FrobeniusThresholds} is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.

@@

However, for the sake of concreteness, we will mostly work in a polynomial ring over a finite field of  characteristic $p>0$.  In fact,  we will work in this context exclusively in this introduction.  Thus, unless otherwise stated, all polynomials and ideals under consideration are regarded as elements in such a ring.  The ideal of this ring generated by its variables is denoted $\idealm$.

>>>>

\begin{abstract}
   This article describes the \emph{Macaulay2} package \emph{FrobeniusThresholds}.
   This package is designed to estimate and calculate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in prime characteristic commutative algebra.
\end{abstract}

@@

Unfortunately, the $F$-pure threshold is typically difficult to calculate, even in many concrete cases.   It is also not so well understood from the perspective of reduction to prime characteristic.   Nevertheless, $F$-pure thresholds have been the focus of intense study over the past 15 years, and the \emph{Macaulay2} package \emph{FrobeniusThresholds} is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.

@@

However, for the sake of concreteness, we will mostly work in a polynomial ring over a finite field of  characteristic $p>0$.  In fact,  we will work in this context exclusively in this introduction.  Thus, unless otherwise stated, all ring elements and ideals under consideration are regarded as elements in such a ring.  The ideal of this ring generated by its variables is denoted $\idealm$.
